### 2017-05-11 paper/evaluation.tex
pass on intro
Added JCTools

\newpage
\section{Objects of Analysis}
\label{sec:subjects}

@@

Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%
AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%

@@

Javaslang (\CodeIn{core})       & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%

%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%

>>>>

\section{Objects of Analysis}
\label{sec:subjects}

@@

Facebook Linkbench    & \entry{4.3m}{98}  & \entry{1.00x}{0\%} & \entry{1.65x}{1.02\%} & \entry{1.59x}{1.02\%} & \entry{}{} & \entry{}{}\\%

AWS SDK Java (\CodeIn{core})  & \entry{3.7m}{847}  & \entry{1.95x}{2.24\%} & \entry{2.47x}{2.77\%} & \entry{3.70x}{4.01\%} & \entry{}{} & \entry{}{}\\%
JCTools (\CodeIn{core})       & \entry{3.6m}{690}  & \entry{4.50x}{0\%} & \entry{3.60x}{0\%} & \entry{18.00x}{0\%} & \entry{}{} & \entry{}{}\\%

@@

Javaslang (\CodeIn{core})     & \entry{1.1m}{17513}  & \entry{1.38x}{0\%} & \entry{1.83x}{0\%} & \entry{1.38x}{0\%} & \entry{}{} & \entry{}{}\\%
%%  & \entry{x.xm}{0}  & \entry{}{\%} & \entry{}{\%} & \entry{}{\%} & \entry{}{} & \entry{}{}\\%
%%OpenMRS Core (\CodeIn{api})  & \entry{15.4m}{3436} & \blankentry{}        & \blankentry{}        & \blankentry{} & \entry{1.5x}{0\%} & \entry{1.7x}{0}\\%
%%Apache Flume (\CodeIn{core}) &  \entry{7.7m}{392}  & \blankentry{}        & \blankentry{}        & \blankentry{}       & \entry{0.9x}{0\%} & \blankentry{} \\%
%%Facebook Archive Linkbench   &  \entry{4.5m}{98}   & \entry{1.0x}{0.2\%}  & \entry{1.6x}{1.2\%}       & \entry{1.0x}{0\%}  & \entry{1.7x}{0.5\%}  & \entry{1.7x}{0.2\%}\\%
%%AWS SDK Java (\CodeIn{core}) &  \entry{3.8m}{847}  & \multicolumn{6}{c}{\Fix{requires investigation}} & \entry{2.2x}{0.1\%} & \entry{3.2x}{2.0\%}\\%
